Higher order unification for free!

### 2024-04-08 paper/main.tex
headers

@@

@@

\subsection{eq and unif}

@@

For reference, \elpiIn{(beta T A R)} reduces away \elpiIn{lam} nodes in head
position in \elpiIn{T} whenever the list \elpiIn{A} provides a corresponding
argument.

@@

\subsection{Logic program simulation}

@@

\subsection{The solution in a nutshell}
\label{sec:nutshell}
A term $s$ is compiled in a term $t$ where every
``problematic'' sub term $p$ is replaced by a fresh unification variable $h$
and an accessory \emph{link} that represent a suspended unification problem
$h \Ue p$. As a result \Ue is ``well behaved'' on $t$, in the sense that
it does not contradict \Eo as it would otherwise do on ``problematic'' terms.
We now define ``problematic'' and ``well behaved'' more formally.

@@

\section{Preliminaries for \Fo{} and \Ho}
\label{sec:lang-spec}
\todo{maybe move here napp beta deref fderef move}

>>>>

\subsection{Preliminaries: \Fo{} and \Ho{}}

@@

\paragraph{Notational conventions}

@@

\subsection{Equational theories an unification}

@@

\todo{move to next section}
For reference, \elpiIn{(beta T A R)} reduces away \elpiIn{lam} nodes in head
position in \elpiIn{T} whenever the list \elpiIn{A} provides a corresponding
argument.

@@

\subsection{The problem: Logic Program Simulation}

@@

\subsection{The solution (in a nutshell)}
\label{sec:nutshell}
A term $s$ is compiled in a term $t$ where every
``problematic'' sub term $p$ is replaced by a fresh unification variable $h$
and an accessory \emph{link} that represent a suspended unification problem
$h \Ue p$. As a result \Ue is ``well behaved'' on $t$, in the sense that
it does not contradict \Eo as it would otherwise do on ``problematic'' terms.
We now define ``problematic'' and ``well behaved'' more formally.

@@

\section{Ground work for \Fo{}, \Ho and the compiler}
\label{sec:lang-spec}
\todo{maybe move here napp beta deref fderef move}
